---
title: "MWF_GaitModels"
author: "Narlon Cassio"
date: "January 13, 2022"
output: 
  pdf_document: 
    toc: yes
    number_sections: yes
    toc_depth: 5
  word_document: 
    toc: yes
    toc_depth: 5
geometry: "left = 1cm, right = 1cm, top = 1cm, bottom = 2.5cm"
header-includes:
- \usepackage{caption}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
editor_options: 
  chunk_output_type: console
---

\newpage

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  fig.height = 5, fig.width = 6, fig.align="center"
)
```

\small

# Loading packages

```{r, }
#------------------------------------------------------------------#
# Loading packages                                              ####
#------------------------------------------------------------------#
library(tidyverse)
library(tableone)
library(gvlma)
library(openxlsx)
library(broom)
library(psych)
library(emmeans)
library(knitr)
library(rstatix)
library(performance)
library(lavaan)
```

# Loading data

```{r, message = FALSE}
#------------------------------------------------------------------#
# Loading data                                                  ####
#------------------------------------------------------------------#
# Outcome and descriptive data
all_data_clean <- read.xlsx("all_data_clean_final.xlsx")
mwf_wm_eroded <- read.xlsx("mwf_merged_eroded.xlsx")

## Adding eroded MWF data for whole-brain
all_data_clean <- left_join(all_data_clean, mwf_wm_eroded)
write.xlsx(all_data_clean, "all_data_clean_final.xlsx")

```

# Data analysis

## Descriptives

```{r, }
# Demographics
kable(digits = 2, caption = "Demographics",
      describe(all_data_clean[c("age", 
                                "height", 
                                "weight",
                                "overall_fall_risk_score")], fast = TRUE, IQR = TRUE))

# Non-normal variables
kable(print(printToggle = FALSE, CreateTableOne(data = all_data_clean, c("bmi", "moca", "mmse"), 
                           includeNA = TRUE), nonnormal = c("bmi","moca", "mmse")))

## Categorical demographics data 
kable(print(printToggle = FALSE, CreateTableOne(data = all_data_clean, c("sex", "fazekas_score", "education_r"))))
kable(print(printToggle = FALSE, 
            CreateTableOne(data = all_data_clean, 
            c("fci_1_arthritis",
              "fci_2_osteoporosis",
              "fci_3_asthma",
              "fci_4_copd_ards_or_emphysema",
              "fci_5_angina",
              "fci_6_congestive_heart_failure_or_heart_disease",
              "fci_7_heart_attack_myocardial_infarct",
              "fci_8_neurological_disease",
              "fci_9_stroke_or_tia",
              "fci_10_peripheral_vascular_disease",
              "fci_11_diabetes_type_i_and_ii",
              "fci_12_upper_gastrointestinal_disease",
              "fci_13_depression",                                
              "fci_14_anxiety_or_panic_disorders",
              "fci_15_visual_impairment",
              "fci_16_hearing_impairment",
              "fci_17_degenerative_disc_disease",
              "fci_18_obesity_and_or_body_mass_index_30",
              "fci_19_thyroid_disease",
              "fci_20_cancer",
              "fci_21_hypertension",
              "fci_total")), noSpaces = TRUE))

## Total Functional commorbidity index
kable(print(printToggle = FALSE, CreateTableOne(data = all_data_clean, c("fci_total"), 
                           includeNA = TRUE), nonnormal = c("fci_total")))

# Myelin water fraction
kable(digits = 3, caption = "Myelin water fraction",
      describe(all_data_clean[c("MWF_TOT_WM_mean","MWF_TOT_WM_eroded_mean",
                             "ALL_mean", 
                             "Ant_CR_mean",
                             "Post_CR_mean",
                             "Sup_CR_mean",
                             "BCC_mean",
                             "GCC_mean",
                             "SCC_mean",
                             "Cingulum_mean", 
                             "Ext_Cap_mean", 
                             "Fornix_mean",
                             "Sag_Strat_mean",
                             "Ant_IC_mean",
                             "Post_IC_mean", 
                             "Retro_IC_mean",
                             "Post_TR_mean",
                             "SLF_mean",
                             "Frontal_WM_all_mean",
                             "Parietal_WM_all_mean")], fast = TRUE, IQR = TRUE))

# Other structural data
kable(print(printToggle = FALSE, CreateTableOne(data = all_data_clean, c("wmh_cm3", "wmh_cm3_lg","eicv_cm3"), 
                           includeNA = TRUE), nonnormal = c("wmh_cm3")))

# Gait measures  
kable(digits = 3, caption = "Gait parameters",
      describe(all_data_clean[c("velocity_ST", 
                                "step_length_avg_ST", 
                                "cycle_time_avg_ST", 
                                "cycle_time_cov_ST",
                                "cycle_time_cov_ST_lg")], fast = TRUE, IQR = TRUE))
```

### Comparing participants between studies

```{r }
all_data_clean <- all_data_clean %>% 
  mutate(cohort = ifelse(str_detect(id, "FALLERS2_..."), "CogMob2", "RVCI"))

kable(print(printToggle = FALSE, CreateTableOne(
  data = all_data_clean, c(
    "age","height", "weight",
    "sex", "fazekas_score", "education_r",
    "bmi", "moca", "mmse","fci_total",
    "fci_1_arthritis",
    "fci_2_osteoporosis",
    "fci_3_asthma",
    "fci_4_copd_ards_or_emphysema",
    "fci_5_angina",
    "fci_6_congestive_heart_failure_or_heart_disease",
    "fci_7_heart_attack_myocardial_infarct",
    "fci_8_neurological_disease",
    "fci_9_stroke_or_tia",
    "fci_10_peripheral_vascular_disease",
    "fci_11_diabetes_type_i_and_ii",
    "fci_12_upper_gastrointestinal_disease",
    "fci_13_depression",                                
    "fci_14_anxiety_or_panic_disorders",
    "fci_15_visual_impairment",
    "fci_16_hearing_impairment",
    "fci_17_degenerative_disc_disease",
    "fci_18_obesity_and_or_body_mass_index_30",
    "fci_19_thyroid_disease",
    "fci_20_cancer",
    "fci_21_hypertension"), 
  includeNA = TRUE, test = TRUE, strata = "cohort"), explain = TRUE, noSpaces = TRUE,
  nonnormal = c("bmi", "moca", "mmse","fci_total")))

```

## Linear models

```{r, }
#------------------------------------------------------------------#
# Regression models                                             ####
#------------------------------------------------------------------#

# Function to summarize lm output
lm_results <- function(x) {
  my_list <- list()
  my_list$Summary <- (summary(x))
  my_list$Assumtions <- (gvlma(x))
  return(my_list)
}

# Creating contrasts for multi-level categorical variables
all_data_clean <- within(all_data_clean, {
  fazekas_c <- C(as.factor(fazekas_score), treatment, 2)
  education_r_c <- C(as.factor(education_r), treatment, 3)
  print(attributes(fazekas_c))
  print(attributes(education_r_c))
})
  
```

\newpage

### Unadjusted

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
## Select variable names for models
predictor_var <- colnames(all_data_clean[c(41:58,136)])
predictor_var %>% kable(col.names = "Predictor variables")

# List to store models
lm_var_mwf_1 = list()

# Run models in loop script
for (var in predictor_var){
  # Formula
  form <- paste("cycle_time_cov_ST_lg", "~", var)

    # Print results to the list
  lm_var_mwf_1[var] <- list(lm(form,
          data = all_data_clean))
}

## Printing models
for (model in lm_var_mwf_1){
  print(formula(model), showEnv = FALSE)
  print(lm_results(model))
  print(check_model(model))
}

```

### Adjusted

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
## Select variable names for models
predictor_var <- colnames(all_data_clean[c(41:58,136)])
predictor_var %>% kable(col.names = "Predictor variables")

# List to store models
lm_var_mwf_2 = list()

# Run models in loop script
for (var in predictor_var){
  # Formula
  form <- paste(
    "cycle_time_cov_ST_lg", "~", var, 
    "+ age + eicv_cm3 + sex + bmi + mmse") # Covariates

    # Print results to the list
  lm_var_mwf_2[var] <- list(lm(form,
          data = all_data_clean))
}

## Printing models
for (model in lm_var_mwf_2){
  print(formula(model), showEnv = FALSE)
  print(lm_results(model))
  print(check_model(model))
}

```

### Adjusted for WMH

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
## Select variable names for models
predictor_var_wmh <- colnames(all_data_clean[c(43,44,48,54)])
predictor_var_wmh %>% kable(col.names = "Predictor variables")

# List to store models
lm_var_mwf_3 = list()

# Run models in loop script
for (var in predictor_var_wmh){
  # Formula
  form <- paste(
    "cycle_time_cov_ST_lg", "~", var, 
    "+ age + eicv_cm3 + sex + bmi + mmse + wmh_cm3_lg") # Covariates

    # Print results to the list
  lm_var_mwf_3[var] <- list(lm(form,
          data = all_data_clean))
}

## Printing models
for (model in lm_var_mwf_3){
  print(formula(model), showEnv = FALSE)
  print(lm_results(model))
  print(check_model(model))
}
```

# Results

## Model summaries

```{r }
## Unadjusted
all_models_unadjusted_var = tibble()

for (model in lm_var_mwf_1){
  output <- rbind(tidy(model, conf.int = TRUE, conf.level = 0.95))[2,]
  output$outcome <-  as.character(model$terms[[2]]) 
  all_models_unadjusted_var <- rbind(all_models_unadjusted_var,output)
}

## Printing estimates
all_models_unadjusted_var %>% 
  arrange(p.value) %>% 
  kable(digits = 3)

```

```{r}
## Adjusted
all_models_adjusted_var = tibble()

for (model in lm_var_mwf_2){
  output <- rbind(tidy(model, conf.int = TRUE, conf.level = 0.95))[2,]
  output$outcome <-  as.character(model$terms[[2]]) 
  all_models_adjusted_var <- rbind(all_models_adjusted_var,output)
}

## Printing estimates
all_models_adjusted_var %>% 
  arrange(p.value) %>% 
  kable(digits = 3)
```

```{r}
## Adjusted for WMH
all_models_adjusted_var_wmh = tibble()

for (model in lm_var_mwf_3){
  output <- rbind(tidy(model, conf.int = TRUE, conf.level = 0.95))[2,]
  output$outcome <-  as.character(model$terms[[2]]) 
  all_models_adjusted_var_wmh <- rbind(all_models_adjusted_var_wmh,output)
}

## Printing estimates
all_models_adjusted_var_wmh %>% 
  arrange(p.value) %>% 
  kable(digits = 3)
```

## Figures

### Gait and MWF

```{r, }
# Cingulum
ggplot(all_data_clean,aes(Cingulum_mean, cycle_time_cov_ST_lg)) +
  geom_point(size = 3, colour = "turquoise2") +
  ggtitle("Cingulum") +
  geom_smooth(method = lm, se = TRUE, colour = "black", fill = "light blue") +
  xlab(NULL) +
  ylab("Cycle time variability (CoV%), \n log-transformed") + 
  scale_x_continuous(breaks = seq(0.00, 0.15, by = 0.02), limits = c(0.00, 0.13)) +
  scale_y_continuous(breaks = seq(0.00, 2.6, by = 0.2), limits = c(0, 2.6)) +
  theme_dark() +
  theme(plot.background = element_rect(fill = "black", colour = NA),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_line(colour = "grey20"),
        panel.grid.minor = element_line(colour = "grey20"),
        plot.title = element_text(size = 17, hjust = 0.5, colour = "white"),
        axis.line = element_blank(),
        axis.title.y = element_text (size = 17, colour = "white"),
        axis.title.x = element_text (size = 17, colour = "white"),
        axis.text = element_text(colour = "white", size = 15))
ggsave("plots/Cingulum_gait.png", width = 7, height = 5)
```

```{r, }
# Superior longitudinal fasciculus
ggplot(all_data_clean,aes(SLF_mean, cycle_time_cov_ST_lg)) +
  geom_point(size = 3, colour = "turquoise2") +
  ggtitle("Superior longitudinal fasciculus") +
  geom_smooth(method = lm, se = TRUE, colour = "black", fill = "light blue") +
  xlab(NULL) +
  ylab("Cycle time variability (CoV%), \n log-transformed") + 
  scale_x_continuous(breaks = seq(0.00, 0.21, by = 0.02), limits = c(0.07, 0.21)) +
  scale_y_continuous(breaks = seq(0.00, 2.6, by = 0.2), limits = c(0, 2.6)) +
  theme_dark() +
  theme(plot.background = element_rect(fill = "black", colour = NA),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_line(colour = "grey20"),
        panel.grid.minor = element_line(colour = "grey20"),
        plot.title = element_text(size = 17, hjust = 0.5, colour = "white"),
        axis.line = element_blank(),
        axis.title.y = element_text (size = 17, colour = "white"),
        axis.title.x = element_text (size = 17, colour = "white"),
        axis.text = element_text(colour = "white", size = 15))
ggsave("plots/SLF_gait.png", width = 7, height = 5)
```

```{r, }
# Posterior corona radiata
ggplot(all_data_clean,aes(Post_CR_mean, cycle_time_cov_ST_lg)) +
  geom_point(size = 3, colour = "turquoise2") +
  ggtitle("Corona radiata, posterior") +
  geom_smooth(method = lm, se = TRUE, colour = "black", fill = "light blue") +
  xlab(NULL) +
  ylab("Cycle time variability (CoV%), \n log-transformed") + 
  scale_x_continuous(breaks = seq(0.00, 0.20, by = 0.02), limits = c(0.07, 0.20)) +
  scale_y_continuous(breaks = seq(0.00, 2.6, by = 0.2), limits = c(0, 2.6)) +
  theme_dark() +
  theme(plot.background = element_rect(fill = "black", colour = NA),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_line(colour = "grey20"),
        panel.grid.minor = element_line(colour = "grey20"),
        plot.title = element_text(size = 17, hjust = 0.5, colour = "white"),
        axis.line = element_blank(),
        axis.title.y = element_text (size = 17, colour = "white"),
        axis.title.x = element_text (size = 17, colour = "white"),
        axis.text = element_text(colour = "white", size = 15))
ggsave("plots/PostCR_gait.png", width = 7, height = 5)
```

```{r, }
# Corpus callosum, body
ggplot(all_data_clean,aes(BCC_mean, cycle_time_cov_ST_lg)) +
  geom_point(size = 3, colour = "turquoise2") +
  ggtitle("Corpus callosum, body") +
  geom_smooth(method = lm, se = TRUE, colour = "black", fill = "light blue") +
  xlab(NULL) +
  ylab("Cycle time variability (CoV%), \n log-transformed") + 
  scale_x_continuous(breaks = seq(0.00, 0.20, by = 0.02), limits = c(0.07, 0.20)) +
  scale_y_continuous(breaks = seq(0.00, 2.6, by = 0.2), limits = c(0, 2.6)) +
  theme_dark() +
  theme(plot.background = element_rect(fill = "black", colour = NA),
        panel.background = element_rect(fill = "black"),
        panel.grid.major = element_line(colour = "grey20"),
        panel.grid.minor = element_line(colour = "grey20"),
        plot.title = element_text(size = 17, hjust = 0.5, colour = "white"),
        axis.line = element_blank(),
        axis.title.y = element_text (size = 17, colour = "white"),
        axis.title.x = element_text (size = 17, colour = "white"),
        axis.text = element_text(colour = "white", size = 15))
ggsave("plots/BCC_gait.png", width = 7, height = 5)
```

\newpage

#### WMH plots

```{r }
### Cingulum
ggplot(all_data_clean, aes(cycle_time_cov_ST_lg, wmh_cm3_lg)) +
  geom_point(aes(col = Cingulum_mean), size = 3) +
  geom_smooth(method = lm, se = TRUE, colour = "black") +
  scale_colour_gradient(low = "yellow", high = "red") + 
  ggtitle(" ") +
  labs(color = "Cingulum,\nMyelin water fraction") +
  ylab("White matter hyperintensity,\nlog-transformed") +
  xlab(" ") +
  theme_light() +
  theme(plot.title = element_text(size = 17, hjust = 0.5),
        legend.position = c(0.80, 0.1),
        legend.direction = "horizontal",
        legend.title = element_text(),
        legend.background = element_blank(),
        axis.title.y = element_text (size = 15),
        axis.title.x = element_text (size = 15),
        axis.text = element_text(colour = "black", size = 13)) +
  guides(colour = guide_colourbar(title.position="top", title.hjust = 0.5, barwidth = 10))
ggsave("plots/Cingulum_wmh.png", width = 7, height = 5)

### SLF
ggplot(all_data_clean, aes(cycle_time_cov_ST_lg, wmh_cm3_lg)) +
  geom_point(aes(col = SLF_mean), size = 3) +
  geom_smooth(method = lm, se = TRUE, colour = "black") +
  scale_colour_gradient(low = "yellow", high = "red")+
  ggtitle(" ") +
  labs(color = "SLF,\nMyelin water fraction") +
  ylab("White matter hyperintensity,\nlog-transformed") +
  xlab(" ") +
  theme_light() +
  theme(plot.title = element_text(size = 17, hjust = 0.5),
        legend.position = c(0.80, 0.1),
        legend.direction = "horizontal",
        legend.title = element_text(),
        legend.background = element_blank(),
        axis.title.y = element_text (size = 15),
        axis.title.x = element_text (size = 15),
        axis.text = element_text(colour = "black", size = 13)) +
  guides(colour = guide_colourbar(title.position="top", title.hjust = 0.5, barwidth = 10))
ggsave("plots/SLF_wmh.png", width = 7, height = 5)

### Posterior corona radiata
ggplot(all_data_clean, aes(cycle_time_cov_ST_lg, wmh_cm3_lg)) +
  geom_point(aes(col = Post_CR_mean), size = 3) +
  geom_smooth(method = lm, se = TRUE, colour = "black") +
  scale_colour_gradient(low = "yellow", high = "red")+
  ggtitle(" ") +
  labs(color = "Corona radiata, posterior,\nMyelin water fraction") +
  ylab("White matter hyperintensity,\nlog-transformed") +
  xlab(" ") +
  theme_light() +
  theme(plot.title = element_text(size = 17, hjust = 0.5),
        legend.position = c(0.80, 0.1),
        legend.direction = "horizontal",
        legend.title = element_text(),
        legend.background = element_blank(),
        axis.title.y = element_text (size = 15),
        axis.title.x = element_text (size = 15),
        axis.text = element_text(colour = "black", size = 13)) +
  guides(colour = guide_colourbar(title.position="top", title.hjust = 0.5, barwidth = 10))
ggsave("plots/PostCR_wmh.png", width = 7, height = 5)

### Corpus callosum, body
ggplot(all_data_clean, aes(cycle_time_cov_ST_lg, wmh_cm3_lg)) +
  geom_point(aes(col = BCC_mean), size = 3) +
  geom_smooth(method = lm, se = TRUE, colour = "black") +
  scale_colour_gradient(low = "yellow", high = "red")+
  ggtitle(" ") +
  labs(color = "Corpus callosum, body,\nMyelin water fraction") +
  ylab("White matter hyperintensity,\nlog-transformed") +
  xlab("Cycle time variability (CoV%), log-transformed") +
  theme_light() +
  theme(plot.title = element_text(size = 17, hjust = 0.5),
        legend.position = c(0.80, 0.1),
        legend.direction = "horizontal",
        legend.title = element_text(),
        legend.background = element_blank(),
        axis.title.y = element_text (size = 15),
        axis.title.x = element_text (size = 15),
        axis.text = element_text(colour = "black", size = 13)) +
  guides(colour = guide_colourbar(title.position="top", title.hjust = 0.5, barwidth = 10))
ggsave("plots/BCC_wmh.png", width = 7, height = 5)

```

\newpage

# Models for other gait variables

## Gait velocity

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
## Select variable names for models
predictor_var <- colnames(all_data_clean[41:58])
predictor_var %>% kable(col.names = "Predictor variables")

# List to store models
lm_vel_mwf_2 = list()

# Run models in loop script
for (var in predictor_var){
  
  # Formula
  form <- paste(
    "velocity_ST", "~", var, 
    "+ age + eicv_cm3 + sex + bmi + mmse") # Covariates

  # Print results to the list
  lm_vel_mwf_2[var] <- list(lm(form,
          data = all_data_clean))
}

```

### Models

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
## Printing models
for (model in lm_vel_mwf_2){
  print(formula(model), showEnv = FALSE)
  print(lm_results(model))
}
```

### Results

```{r }
## Printing estimates
## Adjusted
all_models_adjusted_vel = tibble()

for (model in lm_vel_mwf_2){
  output <- rbind(tidy(model, conf.int = TRUE, conf.level = 0.95))[2,]
  output$outcome <-  as.character(model$terms[[2]]) 
  all_models_adjusted_vel <- rbind(all_models_adjusted_vel,output)
}

## Printing estimates
all_models_adjusted_vel %>% 
  arrange(p.value) %>% 
  kable(digits = 3)

```

## Step length

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
## Select variable names for models
predictor_var <- colnames(all_data_clean[41:58])
predictor_var %>% kable(col.names = "Predictor variables")

# List to store models
lm_step_mwf_2 = list()

# Run models in loop script
for (var in predictor_var){
  
  # Formula
  form <- paste(
    "step_length_avg_ST", "~", var, 
    "+ age + eicv_cm3 + sex + bmi + mmse") # Covariates

  # Print results to the list
  lm_step_mwf_2[var] <- list(lm(form,
          data = all_data_clean))
}

```

### Models

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
## Printing models
for (model in lm_step_mwf_2){
  print(formula(model), showEnv = FALSE)
  print(lm_results(model))
}
```

### Results

```{r }
## Printing estimates
## Adjusted
all_models_adjusted_step = tibble()

for (model in lm_step_mwf_2){
  output <- rbind(tidy(model, conf.int = TRUE, conf.level = 0.95))[2,]
  output$outcome <-  as.character(model$terms[[2]]) 
  all_models_adjusted_step <- rbind(all_models_adjusted_step, output)
}

## Printing estimates
all_models_adjusted_step %>% 
  arrange(p.value) %>% 
  kable(digits = 3)
```

# Multiple comparisons

```{r}
## Computing FDR
all_models_fdr <- rbind(
  (all_models_adjusted_var %>% 
  mutate(outcome = "variability")),

(all_models_adjusted_vel %>% 
  mutate(outcome = "velocity")),

(all_models_adjusted_step %>% 
  mutate(outcome = "step")))

## Adjusting for FDR (assuming 3 tests per predictor)
## Using FDR at alpha = 0.05
all_models_fdr %>% 
  mutate(p.fdr = p.adjust(p.value, method = "fdr")) %>% 
  arrange(p.value) %>% 
  kable(digits = 3)

write.csv(all_models_fdr, "all_models_fdr.csv")
```

# WMH as predictor

## Gait variables

```{r }

all_data_clean <- all_data_clean %>% # centering variables to plot estimates
  mutate(velocity_ST_c = scale(velocity_ST),
         step_length_avg_ST_c = scale(step_length_avg_ST),
         cycle_time_cov_ST_lg_c = scale(cycle_time_cov_ST_lg))

wmh_gait_lm <- list(
  lm(velocity_ST_c ~ wmh_cm3_lg,
          data = all_data_clean),
  
  lm(step_length_avg_ST_c ~ wmh_cm3_lg,
          data = all_data_clean),
  
  lm(cycle_time_cov_ST_lg_c ~ wmh_cm3_lg,
          data = all_data_clean))

```

### Models

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
## Printing models
for (model in wmh_gait_lm){
  print(formula(model), showEnv = FALSE)
  print(lm_results(model))
}
```

### Results

```{r }
## Adjusted
wmh_gait_lm_estimates = tibble()

for (model in wmh_gait_lm){
  output <- rbind(tidy(model, conf.int = TRUE, conf.level = 0.95,))[2,]
  output$rsquared <- summary(model)$r.squared
  output$outcome <-  as.character(model$terms[[2]]) 
  wmh_gait_lm_estimates <- rbind(wmh_gait_lm_estimates, output)
}

## Printing estimates
wmh_gait_lm_estimates %>% 
  arrange(p.value) %>% 
  kable(digits = 3)
```

## MWF variables

```{r }
## Select variable names for models
outcome_var <- colnames(all_data_clean[c(41:58,136)])
outcome_var %>% kable(col.names = "Outcome variables")

# List to store models
wmh_mwf_lm = list()
  
# Run models in loop script
for (var in outcome_var){
  # Formula
  form <- paste(var, "~ wmh_cm3_lg")
  
  # Print results to the list
  wmh_mwf_lm[var] <- list(lm(form,
          data = all_data_clean))
}

```

### Models

```{r, fig.height = 14, fig.width = 10, fig.align="center" }
  ## Printing models
for (model in wmh_mwf_lm){
  print(formula(model), showEnv = FALSE)
  print(lm_results(model))
}
```

### Results

```{r }
## Printing estimates
wmh_mwf_lm_estimates = tibble()

for (model in wmh_mwf_lm){
  output <- rbind(tidy(model, conf.int = TRUE, conf.level = 0.95))[2,]
  output$rsquared <- summary(model)$r.squared
  output$outcome <-  as.character(model$terms[[2]]) 
  wmh_mwf_lm_estimates <- rbind(wmh_mwf_lm_estimates, output)
}

## Printing estimates
wmh_mwf_lm_estimates %>% 
  arrange(p.value) %>% 
  kable(digits = 3)
```

### Plots

```{r}
wmh_gait_lm_estimates %>% 
  mutate(p.value_sig = ifelse(p.value < 0.001, paste("p < ", 0.001),
                       ifelse(p.value < 0.05,paste("p =",round(p.value, 3)),"")),
    outcome = str_replace_all(outcome, c(
    "velocity_ST_c" = "Gait velocity",
    "step_length_avg_ST_c" = "Step length",
    "cycle_time_cov_ST_lg_c" = "Cycle time variability"))) %>%
  ggplot(aes(x = reorder(outcome, p.value), estimate, colour = outcome)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.2, colour = "black") +
  geom_point(size = 3) +
  geom_hline(yintercept = 0, size = 0.2, linetype = "dashed") +
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1), limits = c(-0.8, 0.8), n.breaks = 9) +
  coord_flip() +
  xlab(NULL) +
  ylab("Estimates (95% CI)") +
  geom_text(aes(label = p.value_sig), colour = "black", size = 2.5, vjust = 2.25) +
  theme_light() +
  theme(legend.position = "none",
        axis.text = element_text(colour = "black", size = 10),
        axis.text.y = element_text(face="bold"),
        axis.title = element_text(colour = "black", size = 10))
ggsave("plots/estimates_gait_mwf.png", width = 5, height = 5)

```

```{r, fig.height = 8, fig.width = 8, fig.align="center" }
wmh_mwf_lm_estimates %>% 
  filter(outcome != "MWF_TOT_WM_mean") %>% 
  mutate(p.value_sig = ifelse(p.value < 0.001, paste("p < ", 0.001),
                       ifelse(p.value < 0.05,paste("p =",round(p.value, 3)),"")),
    outcome = str_replace_all(outcome, c(
    "Ant_CR_mean" = "Corona Radiata, anterior",
    "Ant_IC_mean" = "Internal Capsule, anterior",
    "BCC_mean" = "Corpus Callosum, body",
    "Cingulum_mean" = "Cingulum",
    "Ext_Cap_mean" = "External Capsule",
    "Fornix_mean" = "Fornix",
    "GCC_mean" = "Corpus Callosum, genu",
    "MWF_TOT_WM_eroded_mean" = "Whole-brain white matter",
    "Post_CR_mean" = "Corona Radiata, posterior",
    "Sup_CR_mean" = "Corona Radiata, superior",
    "Post_IC_mean" = "Internal Capsule, posterior",
    "Post_TR_mean" = "Thalamic Radiation, posterior",
    "Retro_IC_mean" = "Internal Capsule, retrolenticular",
    "Sag_Strat_mean" = "Sagittal Stratum",
    "SCC_mean" = "Corpus Callosum, splenium",
    "SLF_mean" = "Superior Longitudinal Fasciculus",
    "Frontal_WM_all_mean" = "Frontal white matter",
    "Parietal_WM_all_mean" = "Parietal white matter"))) %>%
  ggplot(aes(x = reorder(outcome, p.value), estimate, colour = outcome)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, size = 0.2, colour = "black") +
  geom_point(size = 3) +
  geom_hline(yintercept = 0, size = 0.2, linetype = "dashed") +
  scale_y_continuous(labels = scales::number_format(accuracy = 0.01), limits = c(-0.05, 0.05), n.breaks = 9) +
  coord_flip() +
  xlab(NULL) +
  ylab("Estimates (95% CI)") +
  geom_text(aes(label = p.value_sig), colour = "black", size = 2.5, vjust = 2.25) +
  theme_light() +
  theme(legend.position = "none",
        axis.text = element_text(colour = "black", size = 10),
        axis.text.y = element_text(face="bold"),
        axis.title = element_text(colour = "black", size = 10))
ggsave("plots/estimates_wmh_mwf.png", width = 8, height = 8)

```
